Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-12 manuscript/manuscript.Rmd
updates quadrat information for population model

We modeled each grass population based on two levels of data: individual and quadrat (Fig. 2). The individual data is the "raw" data. For the quadrat-level we data we simply sum individual basal cover for each quadrat by species. This is equivalent to a near-perfect census of quadrat percent cover because previous analysis shows that measurement error at the individual-level is small [@Chu2014]. Based on these two datasets we can compare population models built using individual-level data and aggregated, quadrat-level data. At the individual level we explicitly model three vital rates: growth (13 year-to-year transitions, 29 quadrats, 18,730 records), survival (13 years, 33 quadrats, 29,353 records), and recruitment (13 years, 33 quadrats, 304 records). At the quadrat level we model population growth as change in percent cover of quadrats with non-zero cover in year *t* and in year *t-1* (13 year-to-year transitions, 19 quadrats, 784 records). For modeling population growth at the quadrat level we ignore within-quadrat extirpation and colonization events because they are very rare in our time series ($N=9$ and $N=10$, respectively, across all species). Given the broad spatial distribution of the quadrats we are studying, it is safe to assume that these events are in fact rare enough to be ignored for our purposes.

>>>>

We modeled each grass population based on two levels of data: individual and quadrat (Fig. 2). The individual data is the "raw" data. For the quadrat-level we data we simply sum individual basal cover for each quadrat by species. This is equivalent to a near-perfect census of quadrat percent cover because previous analysis shows that measurement error at the individual-level is small [@Chu2014]. Based on these two datasets we can compare population models built using individual-level data and aggregated, quadrat-level data. At the individual level we explicitly model three vital rates: growth (13 year-to-year transitions, 29 quadrats, 18,730 records), survival (13 years, 33 quadrats, 29,353 records), and recruitment (13 years, 33 quadrats, 304 records). At the quadrat level we model population growth as change in percent cover of quadrats with non-zero cover in year *t* and in year *t-1* (13 year-to-year transitions, 29 quadrats, 866 records). For modeling population growth at the quadrat level we ignore within-quadrat extirpation and colonization events because they are very rare in our time series ($N=16$ and $N=13$, respectively, across all species). Given the broad spatial distribution of the quadrats we are studying, it is safe to assume that these events are in fact rare enough to be ignored for our purposes.
